How to use replication assignments for teaching integrity in empirical archaeology

### 2019-08-17 README.Rmd
resubmit after peer reviews

- [:file_folder: paper](/analysis/paper): R Markdown source document for manuscript. Includes code to reproduce the figures and tables generated by the analysis. It also has a rendered version, `paper.docx`, suitable for reading (the code is replaced by figures and tables in this file)    
- [:file_folder: data](/analysis/data): Data used in the analysis.  
- [:file_folder: figures](/analysis/figures): Plots and other illustrations

>>>>

- [:file_folder: paper](/analysis/paper): R Markdown source document for manuscript. Includes code to reproduce the figures and tables generated by the analysis. It also has a rendered version, `paper.docx`, suitable for reading (the code is replaced by figures and tables in this file)    
- [:file_folder: data](/analysis/data): Data used in the analysis.  
- [:file_folder: figures](/analysis/figures): Plots and other illustrations
- [:file_folder: figures](/analysis/supplementary-materials): Supplementary materials including the assignment instructions that we used with the students, and two completed assignments submitted by students in this class.

### 2019-08-17 analysis/paper/paper.Rmd
resubmit after peer reviews

This brief survey demonstrates that replication assignments are widely known in economics, psychology, political science, neuroscience and other fields [e.g. @roettger2018towards] . Common elements include group work, use of open source software and services to make the replication results openly accessible to anyone, and a scaffolded, stepwise approach to the task to ensure that students receive instructor support at multiple stages in the assignment. To the best of our knowledge, replication assignments are not common in archaeology programs, although the tools and data structures are generally similar to other social sciences. We posted a message to the Society of American Archaeology Teaching Archaeology Interest Group e-community on 27 May 2019 to ask for examples of replication assignments used in teaching archaeology, and received no replies from anyone teaching with replication. More broadly in archaeology, replication and reproducibility has received limited, but growing, attention. Elsewhere, we have documented recent rapid increases in the number of publications that include code and data to enable readers to reproduce the published results [@Marwick_Schmidt_2019]

>>>>

This brief survey demonstrates that replication assignments are widely known in economics, psychology, political science, neuroscience and other fields [e.g. @roettger2018towards] . Common elements include group work, use of open source software and services to make the replication results openly accessible to anyone, and a scaffolded, stepwise approach to the task to ensure that students receive instructor support at multiple stages in the assignment. To the best of our knowledge, replication assignments are not common in archaeology programs, although the tools and data structures are generally similar to other social sciences. We posted a message to the Society of American Archaeology Teaching Archaeology Interest Group e-community on 27 May 2019 to ask for examples of replication assignments used in teaching archaeology, and received no replies from anyone teaching with replication. More broadly in archaeology, replication and reproducibility has received limited, but growing, attention. Elsewhere, we have documented recent rapid increases in the number of publications that include code and data to enable readers to reproduce the published results [@Schmidt2019]
